Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-30 Ben_Manuscripts/transport/Draft.tex
Revisions after full read-through

  All of these separations are possible in part with current commercial
  membrane separation techniques but suffer from serious drawbacks. Currently,
  reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
  separations of small molecules.~\cite{warsinger_review_2018} RO membranes are
  typically dense polymer matrices that separate solutes based on differences in
  their solubility and permeability in the membrane
  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
  selective separations, high feed pressures, and thus large amounts of energy,
  are necessary in order to generate a useful permeate
  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
  nm-sized pores which can give the same permeate flux as RO with lower applied
  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
  size, limiting selectivity.~\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

@@

  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membranes are nanostructured membranes that may be able to achieve the
  selectivity of RO membranes while maintaining the high permeability
  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II} LLC
  phase is formed when LLC monomers self-assemble into hexagonally packed
  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
  cross-linking of the hexagonal mesophases yields a mechanically strong
  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
  enforce a strict molecular-size cut-off while the hexagonal geometry is 
  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
  because the LLC monomers are salts, Donnan exclusion plays a role in 
  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
%  Zhou et al. demonstrated complete rejection
%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
%  membranes.~\cite{zhou_supported_2005}

@@

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can provide detailed descriptions of
  small solute transport within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations. In our previous work, we used MD simulations to 
  determine the most likely structure of the hexagonal phase formed by the monomer
  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques for equilibrating the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ortho_view.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{top_view.pdf}
  \caption{}
  \end{subfigure}
  \caption{In both figures, water molecules that occupy the pores are colored blue,
  the hydrophilic head groups of the LLC monomers are colored orange with all else
  colored gray. (a) Membrane pores are approximately straight and (b) are packed 
  hexagonally.}\label{fig:membrane_rendering}
  \end{figure}

  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
  the membrane in which solutes are placed. 
  We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order to avoid studying charge species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75. Assuming that the pKa of gallic acid is similar 
  to NaGA3C11, it is possible for our sodium salted monomer to exist at the 
  same time as protonated acetic acid. In any case, we are more interested 
  in mechanisms of interaction with specific chemical functionality more than 
  the behavior of specific molecules.

@@

    \hline
  \end{tabular}
%  \end{minipage}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors corresponds to solute groupings
  and are used in many plots. Blue corresponds to simple alcohols, red to 
  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.}\label{table:abbreviations}
  \end{table}

@@

  We then present our efforts to understand how small molecules, 
  including water, partition within the pores. From a macroscopic perspective,
  it might make sense to hypothesize that the water and polar solutes spend
  their time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We then study the gradient in composition of solutes and 
  water and any resultant influence it might have on mechanistic properties.

@@

  We investigate the differences in solute motion, specifically its mean 
  squared displacement (MSD), based on a solute's size, shape and chemical
  functionality. We will study the interactions between solutes, the membrane,
  and water in order to determine which mechanism or mechanisms dominate.

  There are also a couple of questions that this study that are beyond the 
  scope of this study. First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will remain roughly
  the same regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. However, this information is not needed
  to understand the mechanistic details in various membrane regions; 
  This work represents a starting point for observing the types of interactions
  which occur between isolated solutes and the membrane.

@@

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition. We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region.

@@

  To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
  center of each pore of the equilibrated cross-linked configuration. Our choice of 6
  solutes per pore provided a balance of a useful amount of data for generating 
  statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations
  with pressure controlled by the Parrinello-Rahman barostat.

@@

  We measured the time-averaged $z$-direction mean squared displacement (MSD) of the
  centers of mass (COM) of each solute over the course of 1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

@@

  The $z$-direction MSD of water in the 10 wt\% system is linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured particle displacement in one dimension.

@@

  In order to determine an effective radius for each solute, we divided in 
  half the maximum pairwise distance between atoms of each solute over the course of
  a 2.5 ns simulation of solutes dissolved in a cubic box of water. Each box 
  consisted of about 2100 water molecules and 6 solutes. Although there exist
  more involved methods for determining the hydrodynamic radius~\cite{schultz_determination_1961},
  we chose to use a simpler and more intuitive metric since we are only interested
  in observing trends in the solute mean squared displacement as a function
  of solute size.

@@

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement the $z$-direction.
  We reported the standard error in the average hop lengths by 
  bootstrapping the empirical distribution of observed
  hop lengths.\cite{efron_introduction_1994}
  % BJC: could add more detail about which algorithm and cost function
  % penalty I used. Seems unnecessary since it is all in my code.
  %MRS4: I would put in supporting.

  We determined the average frequency of hops by dividing the total number of 
  hops by the total length of the simulation. We used the frequency of
  hops per 1000 ns as the $\lambda$ parameter in a Poisson distribution.
  We calculated the 1--$\sigma$ confidence intervals of the probability % BJC: not sure best way to write 1-sigma CI
  distribution of hops per 1000 ns based on the corresponding Poisson 
  cumulative distribution function and scaled them to a per--nanosecond basis.

@@

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  package which allows us to directly check the validity of identified hydrogen bonds.
  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
  show that our conclusions are insensitive to this definition within a 
  reasonable range of distances and angles. We determined the average percentage
  of solutes which actively participated in a hydrogen bond interaction with 
  monomers each frame. We only counted unique solute--monomer hydrogen bond 
  interactions, meaning solutes that hydrogen bond more than once simultaneously were classified as a
  single pairing event. We determined the standard error of this calculation
  by bootstrapping over each solute's trajectory. For each bootstrap trial,
  we randomly chose 24 solutes with replacement and calculated the average
  active solute-monomer hydrogen bonds per frame.

@@

  We quantified the coordination of solute constituent atoms with sodium ions.
  For each frame, we counted the number of coordinated molecules to a
  given solute atom based on a distance cut-off. Using four different methods,
  Rowley and Roux observed peaks in the radial distribution function for sodium
  coordinated with water at an O--Na distance of between 2.3 and 2.5 \AA.
  \cite{rowley_solvation_2012} We used 2.5 \AA~as the distance cut-off. We 
  found that this approach is more useful than calculating the 3D spherical
  radial distribution function because it gives detailed frame-by-frame 
  information rather than an average.

  Using our procedure we found that sodium ions in a solution of TIP3P water
  coordinate with an average of 3.6 water molecules. We created a 4 x 4 x 4
  nm cubic box of water with the GROMACS tool, \texttt{gmx solvate}. We used
  \texttt{gmx genion} to replace water molecules with sodium and chloride 
  ions in order to create a 0.1 M NaCl solution. We let the system simulate
  for 5 ns and reported the average number of coordinated water molecules 
  per frame after discarding the first nanosecond of simulation.

  We determined the average percentage of solutes actively coordinated to
  a sodium ion each frame. Our calculation procedure is analogous to that for
  solute-monomer hydrogen bond interactions outlined in the previous section.

@@

  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
  % me maybe half a day to implement and generate results. Not sure if necessary though since
  % I'm just going to say that I don't know what distribution it is and we are going to
  % use a percentile.
  % MRS4: maybe while we are waiting for review.
  Hydrogen bond lifetimes appear to be distributed according to a power law or an
  exponential function. A number of researchers provide evidence that supports a 
  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
  studies were done on extremely short timescales relative to ours, outputting positions
  every time step. Voloshin et al. studied hydrogen bonding on multiple timescales and 
  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
  Due to memory limitations, we could not collect data frequently enough to provide a
  %MRS4: tweaking to 
  sufficient answer to this question so when comparing solutes, we use the 95\textsuperscript{th} 
  percentile of hydrogen bond dwell times. This places emphasis on solutes with 
  long dwell times. We reported the standard error of this calculation by bootstrapping
  the distribution of dwell times.

@@

  We measured the average radial distance of each solute of interest 
  from the pore centers. We binned the radial distances and then 
  normalized by the volume of the annulus defined by the bin edges.
  We generated 1-$\sigma$ confidence intervals by bootstrapping the 
  RDFs of each individual solute 200 times. For each solute, we obtained
  an RDF averaged over the entire simulation trajectory. We randomly 
  chose solute RDFs with replacement and averaged them for each bootstrap
  trial. This approach assumes that solute positions are uncorrelated to
  other solutes which we believe is valid due to the low degree of 
  interaction between solutes described in Section~\ref{method:system_setup}.

  Although the pores are often described as straight, they have a
  small degree of tortuosity which disrupts the RDF calcuation. We 
  tried to mitigate the effects of tortuosity by calculating the RDF
  with respect to splines that run through the pore centers. See
  Section~\ref{S-section:splines} of the Supporting Information for 
  a graphical illustration. Each spline consists of 10 points, equally
  spaced in the $z$-direction, whose ($x$, $y$) coordinates are defined
  based on the center of mass of all head groups closest, in $z$, to the
  given point. When calculating RDFs, the radial distance from the pore 
  center is based on the distance between the solute center-of-mass and
  the linearly interpolated ($x$, $y$) coordinates of the pore center 
  calculated based on the closest two spline points. Using the splines, 
  we calculated the tortuosity of the pores by calculating the ratio 
  $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is the 
  length of the unit cell in the $z$-direction. The average tortuosity
  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt\%
  water systems respectively.

  In all RDF plots, we include the average RDF of the head groups as a 
  reference. The head group RDF shown is the average of the head group
  RDFs for each solute system in the plot. We generated 1-$\sigma$ 
  confidence intervals by bootstrapping the RDFs in the same way we did
  the solutes. We scaled the head group RDF so that it would be visible
  next to solute RDFs.

@@

  Before beginning the analysis of solute transport behavior, it is important to
  elucidate the topology of the membrane pores in solvated systems.

>>>>

  All of these separations are possible in part with current commercial
  membrane separation techniques but suffer from serious drawbacks. Currently,
  reverse osmosis (RO) and nanofiltration (NF) dominate commercial membrane
  separations of small molecules.~\cite{warsinger_review_2018} RO membranes are
  typically dense polymer matrices that separate solutes based on differences in
  their solubility and permeability in the membrane
  material.~\cite{fritzmann_state---art_2007} Although they can perform highly
  selective separations, high feed pressures, and thus large amounts of energy,
  are necessary in order to generate a useful permeate
  flux.~\cite{van_der_bruggen_review_2003} NF membranes have well-defined
  nm-sized pores which can give the same permeate flux as RO with lower applied
  pressure.~\cite{hilal_comprehensive_2004} However, the pores are not uniform in
  size, limiting their selectivity.~\cite{werber_materials_2016}.
%  Therefore, multiple membrane passes may be necessary in order to achieve 
%  high selectivity.

@@

  Cross-linked H\textsubscript{II} phase lyotropic liquid crystal (LLC) 
  membranes are nanostructured membranes that may be able to achieve the
  selectivity of RO membranes while maintaining the high permeability
  of NF membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
  phase is formed when LLC monomers self-assemble into hexagonally packed
  and uniform-sized pores.~\cite{smith_ordered_1997} Alignment and subsequent
  cross-linking of the hexagonal mesophases yields a mechanically strong
  membrane.~\cite{feng_scalable_2014,feng_thin_2016} The uniform-sized pores
  enforce a strict molecular-size cut-off while the hexagonal geometry is 
  ideal for high permeability.~\cite{zhou_supported_2005} Additionally, 
  because the LLC monomers are salts, Donnan exclusion plays a role in 
  rejection of charged molecules upon pore entry.~\cite{donnan_theory_1995}
%  Zhou et al. demonstrated complete rejection
%  of solutes larger than 1.2 nm in size for H\textsubscript{II} LLC coated
%  membranes.~\cite{zhou_supported_2005}

@@

  Molecular dynamics (MD) simulations can give us mechanistic insights with 
  atomistic resolution so that we can provide detailed descriptions of
  small solute transport within LLC membrane nanopores and intelligently design new membranes for 
  solute-specific separations. In our previous work, we used MD simulations to 
  determine the most likely structure of the hexagonal phase formed by the monomer
  Na-GA3C11, expanding upon the most recent experimental characterization.~\cite{coscia_understanding_2018,feng_thin_2016}
  We developed techniques to simulate the hexagonal phase formed by neat 
  monomer as well as with varying amounts of water in the pores.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{ortho_view.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{top_view.pdf}
  \caption{}
  \end{subfigure}
  \caption{In both figures, water molecules that occupy the pores are colored blue,
  the hydrophilic head groups of the LLC monomers are colored orange with all else
  colored gray. We expect that transport will be primarily determined by solute
  behavior within the pores. (a) Membrane pores are approximately straight and (b)
  are packed hexagonally.}\label{fig:membrane_rendering}
  \end{figure}

  In this work, we have studied the transport mechanisms exhibited by 20 
  uncharged polar solutes with varying size, chemical functionality and hydrophilic 
  character. Figure~\ref{fig:membrane_rendering} shows an atomistic rendering of
  the membrane in which we placed solutes. We have listed the solutes studied along with the abbreviations that
  we will use in the charts for the remainder of this paper in Table~\ref{table:abbreviations}.
  Note that, in order limit our studies to uncharged species, we have only studied
  %BJC: citations for pKa's
  acetic acid in its protonated form. The pKa of gallic acid is 4.40 while the
  pKa of acetic acid is 4.75.~\cite{chuysinuan_gallic_2009,perrin_pka_1981} 
  Assuming that the pKa of gallic acid is similar to NaGA3C11, it is possible
  for our sodium salted monomer to exist at the same time as protonated acetic
  acid. In any case, we are more interested in mechanisms of interaction with
  specific chemical functionality more than the behavior of specific molecules.

@@

    \hline
  \end{tabular}
%  \end{minipage}
  \caption{Names of solutes along with their molecular structures and the
  abbreviations which we use in this paper. Colors correspond to solute groupings
  and are used in many plots. 
%  Blue corresponds to simple alcohols, red to 
%  diols, triols and sugars, green to ketone-like solutes, orange to sulfur-containing
%  solutes and yellow to solutes that can only accept hydrogen bonds but not donate.
  }\label{table:abbreviations}
  \end{table}

@@

  We then present our efforts to understand how water partitions within the pores.
  From a macroscopic perspective, it might make sense to hypothesize that water 
  spends its time exclusively in the tube-like hydrophilic pore region. Our
  previous work showed that there is a gradual compositional transition from
  the hydrophilic to the hydrophobic region which means that solutes may not
  necessarily stay confined to the centers of the pores or even within the 
  pore region. We use this information in order to justify our restriction
  of solute transport studies to just the pore region.

%  We then study the gradient in composition of solutes and 
%  water and any resultant influence it might have on mechanistic properties.

@@

  We investigate the differences in solute motion, specifically its mean 
  squared displacement (MSD), based on a solute's size and chemical
  functionality. We will study the interactions between solutes, the membrane,
  and water in order to determine which mechanism or mechanisms dominate.

  There are also a couple of questions that are beyond the scope of this study.
  First, we will not study the concentration dependence of the observed transport
  rates. Although the average MSD might change with concentration, we are 
  focused on the underlying solute-membrane interactions that lead to the 
  observed transport mechanisms which we conjecture will remain roughly
  the same regardless of concentration. Second, we will not study the chemical potential
  of solutes in the pores, which could give us a better understanding of 
  equilibrium solute partitioning. However, this information is not needed
  to understand the mechanistic details in various membrane regions; 
  this work represents a starting point for observing the types of interactions
  that occur between isolated solutes and the membrane.

@@

  We observed that some water partitions into the distal tail region of our system and therefore
  built our initial configurations with water in both regions, close to the expected
  equilibrium partition (see Section~\ref{S-section:water_content_equil} of the Supporting
  Information). We define the distal tail region to be ca. 1.5 nm from the pore
  center based on the minimum in the radial distribution of water
  (see Section~\ref{method:rdfs}). The amount of water present in the distal tail region
  may or may not be experimentally consistent but it is necessary for our results to be 
  thermodynamically consistent. We iteratively adjusted the pore radius in our systems
  until the appropriate amount of water fit in the pores after running the GROMACS command
  \texttt{gmx solvate}. We placed water molecules in the distal tail region one at a time
  in random locations with a short energy minimization between each insertion. When 
  studying transport of water in the pores, we limited the calculations to water molecules
  that spent greater than 95\% of their time outside of the distal tail region.

@@

  To study a given solute, we added 6, equally spaced in $z$, solute molecules to the
  center of each pore of the equilibrated cross-linked configuration, for a total of 24
  solutes. Our choice of 6 solutes per pore provides a balance of a useful amount of 
  data for generating statistics and a low degree of interaction between solutes (see 
  Section~\ref{S-section:solute_interaction} of the Supporting Information). At each
  insertion point we placed a randomly oriented solute molecule then ran a short 
  energy minimization. We allowed the solutes to equilibrate for 5 ns using Berendsen
  pressure control then collected transport data over the course of 1 $\mu$s MD simulations
  with pressure controlled by the Parrinello-Rahman barostat.

@@

  We measured the time-averaged $z$-direction (parallel to the pores) mean squared
  displacement (MSD) of the centers of mass (COM) of each solute over the course of 
  1 $\mu$s MD simulations using 
  Equation~\ref{eqn:tamsd}:
  \begin{equation}
	\overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
	\label{eqn:tamsd}
  \end{equation}
  where $\tau$ is the time lag and T is the length of the trajectory~\cite{meroz_toolbox_2015}. 
  The MSD, in standard treatments, grows according to Equation~\ref{eqn:msd_form}:
  \begin{equation} 
	\langle z^2(t) \rangle = K_{\alpha}t^\alpha
	\label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_\alpha$ is the generalized diffusion 
  coefficient. A value of $\alpha < 1$ indicates a subdiffusive process, while a value 
  of $\alpha = 1$ and $\alpha > 1$ is characteristic of Brownian and superdiffusive
  motion respectively.
    % MRS1: time vs. ensemble MSD better in follow-up paper.
    % BJC2: I think it makes sense to mention, otherwise it looks like we don't 
    % fully understand the theory since I talk about subdiffusion in terms of 
    % alpha which is always calculated based on ensemble MSD unless we know for sure that
    % the system is ergodic (which it isn't the case for CTRW)
  In practice, $\alpha$ corresponds to the growth of the \textit{ensemble} MSD given
  by Equation~\ref{eqn:ensemble_msd}~\cite{meroz_toolbox_2015}:
  \begin{equation}
	\langle z^2(t) \rangle = \langle z(t) - z(0) \rangle
	\label{eqn:ensemble_msd}
  \end{equation}
  Since the ensemble MSD is calculated with respect to a reference position, it carries
  some dependence on its starting point. The time-averaged MSD averages over all possible
  time lags of a given length, effectively eliminating any initial configuration 
  dependence and generating	an increased number of observations. For ergodic systems, 
  both types of MSDs will be equal. Since we have a small number of solutes with which to
  generate statistics and because we are not calculating values of $\alpha$ for this 
  particular study,	we will only use the time-averaged MSD.

@@

  The $z$-direction MSD of water in the 10 wt\% system \textit{is} linear. Therefore, for
  the purpose of comparison, we calculated its diffusion constant by fitting a line
  to the linear region of the MSD curve.~\cite{maginn_best_2018}. The diffusion constant
  is then equal to $m/2$ where $m$ is the slope of the linear fit. The slope is divided
  by 2 (rather than 6) because we only measured particle displacement in one dimension.

@@

  In order to determine an effective radius for each solute, we divided in 
  half the maximum pairwise distance between atoms of each solute over the course of
  a 2.5 ns simulation of solutes dissolved in a cubic box of water. Each box 
  consisted of about 2100 water molecules and 6 solutes. Although there exist
  more involved methods for determining the hydrodynamic radius~\cite{schultz_determination_1961},
  we chose to use a simpler and more intuitive metric since we are only interested
  in observing trends in the solute MSD as a function
  of solute size.

@@

  In order to measure the length of hops, we first needed to detect
  when they occurred. We used an off-line change point detection 
  algorithm, implemented in the python package \texttt{ruptures}
  \cite{truong_ruptures:_2018}, in order to determine at which 
  points hops occurred in the time series of each solutes' COM. We
  used the 3 dimensional COM positions of each solute, rather than
  just the $z$-direction, in order to detect lateral hops. However,
  hop lengths are reported as their displacement in the $z$-direction.
  We reported the standard error in the average hop lengths by 
  bootstrapping the empirical distribution of observed
  hop lengths.\cite{efron_introduction_1994}
  % BJC: could add more detail about which algorithm and cost function
  % penalty I used. Seems unnecessary since it is all in my code.
  %MRS4: I would put in supporting.

  We determined the average frequency of hops by dividing the total number of 
  hops by the total length of the simulation. We used the frequency of
  hops per 1000 ns as the $\lambda$ parameter in a Poisson distribution.
  We calculated the 1$\sigma$ confidence intervals of the probability % BJC: not sure best way to write 1-sigma CI
  distribution of hops per 1000 ns based on the corresponding Poisson 
  cumulative distribution function and scaled them to a per--nanosecond basis.

@@

  Based on the geometric criteria proposed by Luzar and Chandler 
  \cite{luzar_effect_1996}, we determined a hydrogen bond to exist if the
  distance between the donor, D, and acceptor, A, atoms is less than 
  3.5 \AA~and the angle formed by D--H$\cdot\cdot\cdot$A is less than 30\degree. Attempts
  to describe a hydrogen bond in the context of molecular simulations has
  yielded a number of definitions with no true consensus 
  \cite{prada-gracia_quest_2013} especially since the geometry of hydrogen
  bonds has some dependence on the system being studied. The definition of
  Luzar and Chandler is easily visualized for trajectories using the 
  \texttt{hbonds} representation of the Visual Molecular Dynamics (VMD) software 
  package which allows us to directly check the validity of identified hydrogen bonds.
  In Section~\ref{S-section:hbond_sensitivity} of the Supporting Information, we
  show that our conclusions are insensitive to this definition within a 
  reasonable range of distances and angles.

  We determined the average percentage of solutes
  which actively participated in a hydrogen bond interaction with monomers 
  each frame. Unless noted otherwise, we only counted unique solute--monomer
  hydrogen bond interactions, meaning solutes that hydrogen bond more than 
  once simultaneously were classified as a single pairing event. We determined
  the standard error of this calculation by bootstrapping over each solute's 
  trajectory. For each bootstrap trial, we randomly chose 24 solutes with 
  replacement and calculated the average active solute--monomer hydrogen bonds per frame.

@@

  We quantified the coordination of solute constituent atoms with sodium ions.
  For each frame, we counted the number of coordinated molecules to a
  given solute atom based on a distance cut-off. Using four different methods,
  Rowley and Roux observed peaks in the radial distribution function for sodium
  coordinated with water at an O--Na distance of between 2.3 and 2.5 \AA.
  \cite{rowley_solvation_2012} We used 2.5 \AA~as the distance cut-off in our
  calculations. We found that this approach is more useful than calculating 
  the 3D spherical radial distribution function because it gives detailed 
  frame-by-frame information rather than an average.

  Using our procedure, we found that sodium ions in a solution of TIP3P water
  coordinate with an average of 3.6 water molecules. We created a 4 x 4 x 4
  nm cubic box of water with the GROMACS tool, \texttt{gmx solvate}. We used
  \texttt{gmx genion} to replace water molecules with sodium and chloride 
  ions in order to create a 0.1 M NaCl solution. We let the system simulate
  for 5 ns and reported the average number of coordinated water molecules 
  per frame after discarding the first nanosecond of simulation.

  We determined the average percentage of solutes actively coordinated to
  a sodium ion each frame. Our calculation procedure is analogous to that for
  solute--monomer hydrogen bond interactions outlined in the previous section.

@@

  % BJC: Clauset has an easily understood test for exponential versus power law. Would take
  % me maybe half a day to implement and generate results. Not sure if necessary though since
  % I'm just going to say that I don't know what distribution it is and we are going to
  % use a percentile.
  % MRS4: maybe while we are waiting for review.
  Hydrogen bond lifetimes appear to be distributed according to a power law or an
  exponential function (see Figure~\ref{S-fig:lifetime_distributions} of the 
  Supporting Information). A number of researchers provide evidence that supports a 
  power law distribution~\cite{starr_fast_1999,martiniano_insights_2013}. However, these
  studies were done on extremely short timescales relative to ours, outputting positions
  every time step. Voloshin et al. studied hydrogen bonding on multiple timescales and 
  observed exponential behavior on the longest timescales~\cite{voloshin_hydrogen_2009}. 
  Due to memory limitations, we could not collect data frequently enough to provide a
  sufficient answer to this question so when comparing solutes, we use the 95\textsuperscript{th} 
  percentile of hydrogen bond dwell times. This places emphasis on solutes with 
  long dwell times. We reported the standard error of this calculation by bootstrapping
  the distribution of dwell times.

@@

  We measured the average radial distance of each solute of interest 
  from the pore centers. We binned the radial distances and then 
  normalized by the volume of the annulus defined by the bin edges.
  We generated 1$\sigma$ confidence intervals by bootstrapping the 
  RDFs of each individual solute 200 times. For each solute, we obtained
  an RDF averaged over the entire simulation trajectory. We randomly 
  chose solute RDFs with replacement and averaged them for each bootstrap
  trial. This approach assumes that solute positions are uncorrelated to
  other solutes which we believe is valid due to the low degree of 
  interaction between solutes described in Section~\ref{method:system_setup}.

  Although the pores are often described as straight, they have a
  small degree of tortuosity which disrupts the RDF calcuation. We 
  tried to mitigate the effects of tortuosity by calculating the RDF
  with respect to splines that run through the pore centers. See
  Section~\ref{S-section:splines} of the Supporting Information for 
  a graphical illustration. Each spline consists of 10 points, equally
  spaced in the $z$-direction, whose ($x$, $y$) coordinates are defined
  based on the COM of all head groups closest, in $z$, to the
  given point. When calculating RDFs, the radial distance from the pore 
  center is based on the distance between the solute COM and
  the linearly interpolated ($x$, $y$) coordinates of the pore center 
  calculated based on the closest two spline points. Using the splines, 
  we calculated the tortuosity of the pores by calculating the ratio 
  $\dfrac{L}{Z}$ where $L$ is the length of the spline and $Z$ is the 
  length of the unit cell in the $z$-direction. The average tortuosity
  of each pore is 1.03 $\pm$ 0.01 and 1.07 $\pm$ 0.02 in the 5 and 10 wt\%
  water systems respectively.

  In all RDF plots, we include the average RDF of the head groups as a 
  reference. The head group RDF shown is the average of the head group
  RDFs for each solute system in the plot. We generated 1$\sigma$ 
  confidence intervals by bootstrapping the RDFs in the same way we did
  the solutes. We scaled the head group RDF so that it would be in frame
  next to solute RDFs.

@@

  Before beginning our analysis of solute transport behavior, it is important to
  elucidate the topology of the membrane pores in solvated systems.

  In contrast to our previous work with a dry version of this membrane, the 
  region close to the pore center of the 5 and 10 wt\% water systems is 
  primarily filled with water and sodium ions. Figure~\ref{fig:component_densities}
  plots the RDF of each membrane constituent in the dry system as well as the
  5 and 10 wt\% water systems. In dry systems, the pore center is densely 
  filled with sodium ions and head groups. In hydrated systems, water occupies, 
  and is densest, at the center of each pore. The density of sodium ions is 
  somewhat uniform in the pore center of the 5 wt\% water system while it shows
  a maximum closer to the head groups in the 10 wt\% water system. The peak 
  density of sodium ions is not at the pore center in the 10 wt\% water system
  likely because they are still loosely associated with the monomer's carboxylate
  head groups.
